---
title: "Melissa Kline Struhl"
output: md_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(results='asis', echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(rcrossref)
library(glue)
library(here)
```

```{r get-paper-data, warning = FALSE, include = FALSE}
papers <- read.csv(paste0(here::here(), '/published_papers.csv')) %>%
  mutate(across(where(is.character), ~na_if(., "")))

c_papers <- filter(papers, is.na(crossref_broken)) %>%
  mutate(citation_text = unlist(cr_cn(full_doi, format = 'text', style = "apa")))

noc_papers <- filter(papers, crossref_broken=="x") %>%
  mutate(citation_text = manual_citation)

papers <- bind_rows(c_papers, noc_papers) %>%
  mutate(citation_year = str_extract(citation_text, "(20|19)[0-9]{2}")) %>%
  mutate(section = "papers",
         description_1 = as.character(NA),
         start = as.character(NA),
         end = citation_year) %>%
  mutate_all(as.character)
```

```{r get-unformatted-data}
unformatted_entries <- read.csv(paste0(here::here(), '/unformatted_entries.csv')) %>%
  mutate(across(where(is.character), ~na_if(., ""))) %>%
  mutate_all(as.character)
```

```{r bind-entries}
entries <- bind_rows(papers, unformatted_entries) %>%
  arrange(!is.na(end), desc(end))
```

```{r section-formats, include = FALSE}
# From rdatadrivencv package
#' @description Take a position data frame and the section id desired and prints the section to markdown.
#' @param section_id ID of the entries section to be printed as encoded by the `section` column of the `entries` table

print_section <- function(cvtable, section_id, glue_template = "default"){

  # Choose Template
  if(glue_template == "default"){
    glue_template <- "
    
    {timeline}: {title}
    
    {institution}
    
    {description_bullets}
    
    <br>
"
  }
  
    if(glue_template == "single-line"){
    glue_template <- "
    
    {timeline}: {title}, {institution} {description_bullets}
    
    <br>
"
  }
  
  if(glue_template == "citation"){
    glue_template <- "
    {citation_text}
    
    <br>
"  
  }
  
  if(glue_template == "informal_citation"){
    glue_template <- "
    {manual_citation} {link_address}
    
    <br>
"  
  }
  

  # Get relevant data
  section_data <- dplyr::filter(cvtable, section == section_id)
  
  # Transform data for template!
  section_data <- section_data %>%
    unite(
      starts_with('description'),
      col = "description_bullets",
      sep = "\n\n",
      na.rm = TRUE
    ) %>%
    mutate(description_bullets = ifelse(description_bullets != "", paste0("", description_bullets), "\n")) %>%
    mutate(institution = ifelse(is.na(institution),"", institution)) %>%
    mutate(link_address = ifelse(is.na(link), "", paste0("[Link](", link, ")"))) %>%
    mutate(no_start = is.na(start),
      has_start = !no_start,
      no_end = is.na(end),
      has_end = !no_end,
      timeline = case_when(
        no_start  & no_end  ~ "Ongoing",
        no_start  & has_end ~ as.character(end),
        has_start & no_end  ~ paste(start, "- Present"),
        TRUE                ~ paste(start, "-", end)
      ))

  # Print data in template
  print(glue::glue_data(section_data, glue_template))
}
```

**Lookit Executive Director | Research Scientist**

**Brain & Cognitive Sciences Department**

**Massachusetts Institute of Technology**

<br>
This resume was last updated on `r Sys.Date()`.

[Source code](https://github.com/mekline/mekline-cv), based on the [datadrivencv](https://github.com/nstrayer/datadrivencv) and [vitae](https://cran.r-project.org/web/packages/vitae/index.html) r packages.

<br>

#### Contact Info 

- mekline@mit.edu
- github: [@mekline](https://github.com/mekline)
- twitter: [@melissaekline](https://twitter.com/melissaekline)
- [www.melissaklinestruhl.com](www.melissaklinestruhl.com)
- [lookit.mit.edu](https://lookit.mit.edu/)

<br>

#### Interests

- Open, equitable, and robust scientific practices!
- FAIR data sharing and management
- Online experiments for children & families
- Cognitive development & language acquisition

<br>

#### Education

```{r education}
print_section(entries, section_id = "education", glue_template = "default")
```

#### Published Articles 

```{r citations}
print_section(entries, section_id = "papers", glue_template = "citation")
```

#### Other Manuscripts 

##### Preprints

```{r other1}
print_section(entries, section_id = "preprints", glue_template = "informal_citation")
```

##### Preregistrations

```{r other2}
print_section(entries, section_id = "preregistrations", glue_template = "informal_citation")
```

##### Proceedings

```{r other3}
print_section(entries, section_id = "proceedings", glue_template = "informal_citation")
```

#### Conference Posters & Presentations 
```{r conf}
print_section(entries, section_id = "presen_posters", glue_template = "informal_citation")
```


#### Employment 

```{r employment}
print_section(entries, section_id = "employment", glue_template = "default")
```


#### Awards 
```{r award}
print_section(entries, section_id = "awards")
```

#### Teaching 
```{r teach}
print_section(entries, section_id = "teaching", glue_template = "single-line")
```

#### Service
```{r service}
print_section(entries, section_id = "service", glue_template = "single-line")
```



